## Indiana Pacers Shot Chart Code
```

```

```{r}
install.packages("devtools")
library(devtools)
devtools::install_github("abresler/nbastatR")
```


```{r}
# Packages

install.packages("ggplot2")
install.packages("tidyverse")
install.packages("nbastatR")
install.packages("devtools")
install.packages("extrafont")
install.packages("cowplot")
```

```{r}
# Creating Court 

# Creating court and plotting

circle_points = function(center = c(0, 0), radius = 1, npoints = 360) {
  angles = seq(0, 2 * pi, length.out = npoints)
  return(data_frame(x = center[1] + radius * cos(angles),
                    y = center[2] + radius * sin(angles)))
}

# Court Dimenons & lines
width = 50
height = 94 / 2
key_height = 19
inner_key_width = 12
outer_key_width = 16
backboard_width = 6
backboard_offset = 4
neck_length = 0.5
hoop_radius = 0.75
hoop_center_y = backboard_offset + neck_length + hoop_radius
three_point_radius = 23.75
three_point_side_radius = 22
three_point_side_height = 14

# Court themes
court_themes = list(
  light = list(
    court = 'floralwhite',
    lines = '#999999',
    text = '#222222',
    made = '#00bfc4',
    missed = '#f8766d',
    hex_border_size = 1,
    hex_border_color = "#000000"
  ),
  dark = list(
    court = '#000004',
    lines = '#999999',
    text = '#f0f0f0',
    made = '#00bfc4',
    missed = '#f8766d',
    hex_border_size = 0,
    hex_border_color = "#000000"
  ),
  ppt = list(
    court = 'gray20',
    lines = 'white',
    text = '#f0f0f0',
    made = '#00bfc4',
    missed = '#f8766d',
    hex_border_size = 0,
    hex_border_color = "gray20"
)
)

# Function to create court based on given dimensions
plot_court = function(court_theme = court_themes$light, use_short_three = FALSE) {
  if (use_short_three) {
    three_point_radius = 22
    three_point_side_height = 0
  }
  
  court_points = data_frame(
    x = c(width / 2, width / 2, -width / 2, -width / 2, width / 2),
    y = c(height, 0, 0, height, height),
    desc = "perimeter"
  )
  
  court_points = bind_rows(court_points , data_frame(
    x = c(outer_key_width / 2, outer_key_width / 2, -outer_key_width / 2, -outer_key_width / 2),
    y = c(0, key_height, key_height, 0),
    desc = "outer_key"
  ))
  
  court_points = bind_rows(court_points , data_frame(
    x = c(-backboard_width / 2, backboard_width / 2),
    y = c(backboard_offset, backboard_offset),
    desc = "backboard"
  ))
  
  court_points = bind_rows(court_points , data_frame(
    x = c(0, 0), y = c(backboard_offset, backboard_offset + neck_length), desc = "neck"
  ))
  
  foul_circle = circle_points(center = c(0, key_height), radius = inner_key_width / 2)
  
  foul_circle_top = filter(foul_circle, y > key_height) %>%
    mutate(desc = "foul_circle_top")
  
  foul_circle_bottom = filter(foul_circle, y < key_height) %>%
    mutate(
      angle = atan((y - key_height) / x) * 180 / pi,
      angle_group = floor((angle - 5.625) / 11.25),
      desc = paste0("foul_circle_bottom_", angle_group)
    ) %>%
    filter(angle_group %% 2 == 0) %>%
    select(x, y, desc)
  
  hoop = circle_points(center = c(0, hoop_center_y), radius = hoop_radius) %>%
    mutate(desc = "hoop")
  
  restricted = circle_points(center = c(0, hoop_center_y), radius = 4) %>%
    filter(y >= hoop_center_y) %>%
    mutate(desc = "restricted")
  
  three_point_circle = circle_points(center = c(0, hoop_center_y), radius = three_point_radius) %>%
    filter(y >= three_point_side_height, y >= hoop_center_y)
  
  three_point_line = data_frame(
    x = c(three_point_side_radius, three_point_side_radius, three_point_circle$x, -three_point_side_radius, -three_point_side_radius),
    y = c(0, three_point_side_height, three_point_circle$y, three_point_side_height, 0),
    desc = "three_point_line"
  )
  
  court_points = bind_rows(
    court_points,
    foul_circle_top,
    foul_circle_bottom,
    hoop,
    restricted,
    three_point_line
  )
  
  
  court_points <- court_points
  
  # Final plot creation
  ggplot() +
    geom_path(
      data = court_points,
      aes(x = x, y = y, group = desc),
      color = court_theme$lines
    ) +
    coord_fixed(ylim = c(0, 45), xlim = c(-25, 25)) +
    theme_minimal(base_size = 22) +
    theme(
      text = element_text(color = court_theme$text),
      plot.background = element_rect(fill = 'gray20', color = 'gray20'),
      panel.background = element_rect(fill = court_theme$court, color = court_theme$court),
      panel.grid = element_blank(),
      panel.border = element_blank(),
      axis.text = element_blank(),
      axis.title = element_blank(),
      axis.ticks = element_blank(),
      legend.background = element_rect(fill = court_theme$court, color = court_theme$court),
      legend.margin = margin(-1, 0, 0, 0, unit = "lines"),
      legend.position = "bottom",
      legend.key = element_blank(),
      legend.text = element_text(size = rel(1.0))
    )
}

#Pacers Data to be put on shot chart


#Load packages and increase size

library(dplyr)
library(dbplyr)
library(nbastatR)
library(ggplot2)
library(tidyverse)
library(cowplot)
library(extrafont)
Sys.setenv(VROOM_CONNECTION_SIZE = 10 * 1024 * 1024) # Set buffer size to 10 MB

#Load and clean data for each season
pacers_2016 <- teams_shots(teams = "Indiana Pacers", seasons = 2016) %>%
  mutate(x = as.numeric(as.character(locationX)) / 10,
         y = as.numeric(as.character(locationY)) / 10 + hoop_center_y) %>%
  mutate(x = x * -1)  # Flip x-coordinates horizontally

pacers_2017 <- teams_shots(teams = "Indiana Pacers", seasons = 2017) %>%
  mutate(x = as.numeric(as.character(locationX)) / 10,
         y = as.numeric(as.character(locationY)) / 10 + hoop_center_y) %>%
  mutate(x = x * -1)  

pacers_2018 <- teams_shots(teams = "Indiana Pacers", seasons = 2018) %>%
  mutate(x = as.numeric(as.character(locationX)) / 10,
         y = as.numeric(as.character(locationY)) / 10 + hoop_center_y) %>%
  mutate(x = x * -1)  

pacers_2019 <- teams_shots(teams = "Indiana Pacers", seasons = 2019) %>%
  mutate(x = as.numeric(as.character(locationX)) / 10,
         y = as.numeric(as.character(locationY)) / 10 + hoop_center_y) %>%
  mutate(x = x * -1)  

pacers_2020 <- teams_shots(teams = "Indiana Pacers", seasons = 2020) %>%
  mutate(x = as.numeric(as.character(locationX)) / 10,
         y = as.numeric(as.character(locationY)) / 10 + hoop_center_y) %>%
  mutate(x = x * -1)  

pacers_2021 <- teams_shots(teams = "Indiana Pacers", seasons = 2021) %>%
  mutate(x = as.numeric(as.character(locationX)) / 10,
         y = as.numeric(as.character(locationY)) / 10 + hoop_center_y) %>%
  mutate(x = x * -1) 

#Combine data for all seasons
pacers_combined <- bind_rows(pacers_2016, pacers_2017, pacers_2018, pacers_2019, pacers_2020, pacers_2021)

#Create the shot chart
p1 <- plot_court(court_themes$ppt, use_short_three = FALSE) +
  geom_point(data = pacers_combined, aes(x = x, y = y, color = isShotMade, fill = isShotMade), 
             size = 3, shape = 21, alpha = 0.5, stroke = 0.5) +  # Adjust alpha for opacity
  scale_color_manual(values = c("green4", "red3"), aesthetics = "color", 
                     breaks = c("TRUE", "FALSE"), labels = c("Made", "Missed"), name = NULL) +  # Remove legend title
  scale_fill_manual(values = c("green2", "gray20"), aesthetics = "fill", 
                    breaks = c("TRUE", "FALSE"), labels = c("Made", "Missed"), name = NULL) +  # Remove legend title
  scale_x_continuous(limits = c(-27.5, 27.5)) +
  scale_y_continuous(limits = c(0, 45)) +
  theme_minimal(base_size = 16) +  # Adjust the base_size parameter here
  theme(
    text = element_text(color = court_themes$ppt$text),
    plot.background = element_rect(fill = '#000080', color = '#000080'),
    panel.background = element_rect(fill = court_themes$ppt$court, color = court_themes$ppt$court),
    panel.grid = element_blank(),
    panel.border = element_blank(),
    axis.text = element_blank(),
    axis.title = element_blank(),
    axis.ticks = element_blank(),
    legend.background = element_rect(fill = court_themes$ppt$court, color = court_themes$ppt$court),
    legend.margin = margin(-1, 0, 0, 0, unit = "lines"),
    legend.position = "bottom",
    legend.key = element_blank(),
    legend.text = element_text(size = rel(1.0), family = "Comic Sans MS", face = "bold", color = "yellow"),  # Customize legend text
    plot.title = element_text(color = "yellow")  # Change title color to yellow
  ) +
  ggtitle(label = "Indiana Pacers 2016-2021 Seasons") +
  labs(caption = "Midterm Project")

ggdraw(p1) + theme(plot.background = element_rect(fill = "#000080", color = NA)) 

ggsave("Pacers_2016_to_2021_Shot_Chart.png", height = 6, width = 6, dpi = 300)

```
```{r}
#Pacers 2007, 2014, and 2021 individual shot charts
#load packages

library(dplyr)
library(dbplyr)
library(nbastatR)
library(ggplot2)
library(tidyverse)
library(cowplot)
library(extrafont)
Sys.setenv(VROOM_CONNECTION_SIZE = 10 * 1024 * 1024) #Set buffer size to 10 MB


#Load and clean data for each season
pacers_2007 <- teams_shots(teams = "Indiana Pacers", seasons = 2007) %>%
  mutate(x = as.numeric(as.character(locationX)) / 10,
         y = as.numeric(as.character(locationY)) / 10 + hoop_center_y) %>%
  mutate(x = x * -1)  # Flip x-coordinates horizontally

pacers_2014 <- teams_shots(teams = "Indiana Pacers", seasons = 2014) %>%
  mutate(x = as.numeric(as.character(locationX)) / 10,
         y = as.numeric(as.character(locationY)) / 10 + hoop_center_y) %>%
  mutate(x = x * -1) 

pacers_2021 <- teams_shots(teams = "Indiana Pacers", seasons = 2021) %>%
  mutate(x = as.numeric(as.character(locationX)) / 10,
         y = as.numeric(as.character(locationY)) / 10 + hoop_center_y) %>%
  mutate(x = x * -1)  

# Create shot chart for 2007
p_2007 <- plot_court(court_themes$ppt, use_short_three = FALSE) +
  geom_point(data = pacers_2007, aes(x = x, y = y, color = isShotMade, fill = isShotMade), 
             size = 3, shape = 21, alpha = 0.5, stroke = 0.5) +
  scale_color_manual(values = c("green4", "red3"), aesthetics = "color", 
                     breaks = c("TRUE", "FALSE"), labels = c("Made", "Missed"), name = NULL) +
  scale_fill_manual(values = c("green2", "gray20"), aesthetics = "fill", 
                    breaks = c("TRUE", "FALSE"), labels = c("Made", "Missed"), name = NULL) +
  scale_x_continuous(limits = c(-27.5, 27.5)) +
  scale_y_continuous(limits = c(0, 45)) +
  theme_minimal(base_size = 16) +
  theme(
    text = element_text(color = court_themes$ppt$text),
    plot.background = element_rect(fill = '#000080', color = '#000080'),
    panel.background = element_rect(fill = court_themes$ppt$court, color = court_themes$ppt$court),
    panel.grid = element_blank(),
    panel.border = element_blank(),
    axis.text = element_blank(),
    axis.title = element_blank(),
    axis.ticks = element_blank(),
    legend.background = element_rect(fill = court_themes$ppt$court, color = court_themes$ppt$court),
    legend.margin = margin(-1, 0, 0, 0, unit = "lines"),
    legend.position = "bottom",
    legend.key = element_blank(),
    legend.text = element_text(size = rel(1.0), family = "Comic Sans MS", face = "bold", color = "yellow"),
    plot.title = element_text(color = "yellow")
  ) +
  ggtitle(label = "Indiana Pacers 2007 Season") +
  labs(caption = "Midterm Project")

# Print the shot chart for 2007
print(p_2007)

# For 2014
p_2014 <- plot_court(court_themes$ppt, use_short_three = FALSE) +
  geom_point(data = pacers_2014, aes(x = x, y = y, color = isShotMade, fill = isShotMade), 
             size = 3, shape = 21, alpha = 0.5, stroke = 0.5) +
  scale_color_manual(values = c("green4", "red3"), aesthetics = "color", 
                     breaks = c("TRUE", "FALSE"), labels = c("Made", "Missed"), name = NULL) +
  scale_fill_manual(values = c("green2", "gray20"), aesthetics = "fill", 
                    breaks = c("TRUE", "FALSE"), labels = c("Made", "Missed"), name = NULL) +
  scale_x_continuous(limits = c(-27.5, 27.5)) +
  scale_y_continuous(limits = c(0, 45)) +
  theme_minimal(base_size = 16) +
  theme(
    text = element_text(color = court_themes$ppt$text),
    plot.background = element_rect(fill = '#000080', color = '#000080'),
    panel.background = element_rect(fill = court_themes$ppt$court, color = court_themes$ppt$court),
    panel.grid = element_blank(),
    panel.border = element_blank(),
    axis.text = element_blank(),
    axis.title = element_blank(),
    axis.ticks = element_blank(),
    legend.background = element_rect(fill = court_themes$ppt$court, color = court_themes$ppt$court),
    legend.margin = margin(-1, 0, 0, 0, unit = "lines"),
    legend.position = "bottom",
    legend.key = element_blank(),
    legend.text = element_text(size = rel(1.0), family = "Comic Sans MS", face = "bold", color = "yellow"),
    plot.title = element_text(color = "yellow")
  ) +
  ggtitle(label = "Indiana Pacers 2014 Season") +
  labs(caption = "Midterm Project")


print(p_2014)

# For 2021
p_2021 <- plot_court(court_themes$ppt, use_short_three = FALSE) +
  geom_point(data = pacers_2021, aes(x = x, y = y, color = isShotMade, fill = isShotMade), 
             size = 3, shape = 21, alpha = 0.5, stroke = 0.5) +
  scale_color_manual(values = c("green4", "red3"), aesthetics = "color", 
                     breaks = c("TRUE", "FALSE"), labels = c("Made", "Missed"), name = NULL) +
  scale_fill_manual(values = c("green2", "gray20"), aesthetics = "fill", 
                    breaks = c("TRUE", "FALSE"), labels = c("Made", "Missed"), name = NULL) +
  scale_x_continuous(limits = c(-27.5, 27.5)) +
  scale_y_continuous(limits = c(0, 45)) +
  theme_minimal(base_size = 16) +
  theme(
    text = element_text(color = court_themes$ppt$text),
    plot.background = element_rect(fill = '#000080', color = '#000080'),
    panel.background = element_rect(fill = court_themes$ppt$court, color = court_themes$ppt$court),
    panel.grid = element_blank(),
    panel.border= element_blank(),
    axis.text = element_blank(),
    axis.title = element_blank(),
    axis.ticks = element_blank(),
    legend.background = element_rect(fill = court_themes$ppt$court, color = court_themes$ppt$court),
    legend.margin = margin(-1, 0, 0, 0, unit = "lines"),
    legend.position = "bottom",
    legend.key = element_blank(),
    legend.text = element_text(size = rel(1.0), family = "Comic Sans MS", face = "bold", color = "yellow"),
    plot.title = element_text(color = "yellow")
  ) +
  ggtitle(label = "Indiana Pacers 2021 Season") +
  labs(caption = "Midterm Project")

# Print the shot chart for 2021
print(p_2021)

# Save each plot separately
#ggsave("Pacers_2007_Shot_Chart.png", plot = p_2007, height = 6, width = 6, dpi = 300)
#ggsave("Pacers_2014_Shot_Chart.png", plot = p_2014, height = 6, width = 6, dpi = 300)
#ggsave("Pacers_2021_Shot_Chart.png", plot = p_2021, height = 6, width = 6, dpi = 300)

```

    
  
   
3. (30 points) Write and document clean, efficient, reproducible code. Some notes:

   - This code will be viewed by your direct supervisor.
   - The code file should include your code to gather, join, and clean the data; the code to generate the graphic(s) presented; and your commentary on the results (so, a single .rmd file, or an .rmd file that sources an .r file).
   - Your code should be clean, organized, and reproducible. Remove unnecessary/scratch/exploratory code.
   - Your code should be well commented. In particular, any decisions or judgement calls made in the analysis process should be explained/justified. Sections of code should be identified even if not functionalized (including purpose, data/argument inputs, analysis outputs).
   

  
## The Deliverables

1. Upload your report and code file(s) to GitHub by 11:59am (noon) on Friday, March 29.
2. Submit (on Canvas) your report, code, and link to your GitHub repository by 11:59am (noon) on Friday, March 29.
  
  
  
  


